{\indent In contrast to scientific publications, which present research as a linear progression from questions to conclusions, a PhD program is a winding journey with unexpected turns. Throughout this process, I have benefited from the guidance of many amazing scientists. 
	
Francis-Yan Cyr-Racine and Leonidas Moustakas allowed me to work with them at JPL while I was still an undergraduate, during which time I was introduced to the subject matter described in this dissertation. Chuck Keeton was also in the fold, and today I regard him as a sort of `strong-lensing guru'. I am grateful for the opportunity they gave me six years ago, and their continued support today. 

Throughout my PhD, I was truly lucky to have had the opportunity to work closely with two amazing scientists. Simon Birrer started mentoring me at UCLA almost immediately after finishing his own PhD. I imagine it was a challenge to transition so quickly from a student to a supervisor, but it seemed natural for Simon. He devoted a significant amount of his own time to helping me develop, so any success I have is also party his. I have collaborated with Anna since day one. In complicated research problems it can be easy to get distracted by extraneous details, but Anna has a keen eye for the important details others may overlook. Learning from her for six years has made me a better scientist. 

It is difficult to convey just how much I admire my PhD advisor, Tommaso Treu. To the astronomy community as a whole, Tommaso is regarded as a productive, creative, and talented scientist. To me, he is also a role model and a leader. I could not have asked for a better advisor.  

Finally, I am thankful for the support from my amazing parents. It must have been wild listening to me try to choose a career path: from a pilot, to joining the foreign service, and then finally setting down with astrophysics. Through it all, you have supported me, challenged me, and believed in me. As I get older, I realize more and more how lucky I am to have you two as my parents - I could not have done it without you! 
}